---
title: "Adoption of the updated 2023-2024 COVID-19 Vaccine"
bibliography: My Library.bib


output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r setup, include=FALSE}
library(flexdashboard) # always
```

## Intro {.sidebar}

This dashboard showcases the results of a nationally representative survey fielded to 281 US residents as part of the Fall 2023 DACSS Survey Research Methods course. 

The main objective of my research was to understand how Americans feel about the current state of COVID-19 in the US, and how that might influence their perceptions and use of the newest COVID-19 vaccine, released in the Fall of 2023 [@stapletonFall2023DACSS2023].  

You can find the code and data for this dashboard here: https://github.com/reneezale/DataVizProject 


### Nearly half of US respondents have no plans to receive the updated 2023-2024 COVID-19 Vaccine.


```{r}
readRDS("VaxStatusBarChart.rds")
```


### Respondents vaccinated with the new COVID-19 vaccine are 7 years older, on average, than unvaccinated respondents. 

```{r}
readRDS("VaxAgeHistDuo2.rds")
```

### Respondents who identify as liberal are the most likely to have received the updated vaccine, while conservatives are the most likely to say they have no plans to receive it. 

```{r}
readRDS("StackedBar2.rds")
```

### Region does not appear to have as strong of a relationship to vaccination attitudes as political affiliation. There is no region that stands out as strongly for or against the vaccine.  

```{r}
readRDS("RegionVaxMap.rds")
```

### References

You can find the code and data for this dashboard here: https://github.com/reneezale/DataVizProject  

Survey Data Source: @stapletonFall2023DACSS2023

