---
title: "Adoption of the updated 2023-2024 COVID-19 Vaccine"
#bibliography: testVisual.bib
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r setup, include=FALSE}
library(flexdashboard) # always
```

## Intro {.sidebar}

This dashboard showcases the results of a nationally representative survey fielded to 282 US residents as part of the Fall 2023 DACSS Survey Research Methods course. 

The main objective of my research was to understand how Americans feel about the current state of COVID-19 in the US, and how that might influence their perceptions and use of the newest COVID-19 vaccine, released in the Fall of 2023.  

You can find the code and data for this dashboard here: https://github.com/reneezale/DataVizProject 


### Nearly half of US respondents have no plans to receive the updated 2023-2024 COVID-19 Vaccine.


```{r}
readRDS("VaxStatusBarChart.rds")
```


### The mean age of those who have received the updated COVID-19 vaccine is 52...

```{r}
readRDS("VaxAgeHistFinal.rds")
```

### ...While those who have no plans to receive the updated vaccine are slightly younger, with an average age of 47. 

```{r}
readRDS("VaxAgeHistFinalNoVax.rds")
```

### Respondents who identify as liberal are the most likely to have received the updated vaccine, while conservatives are the most likely to say they have no plans to receive it. 

```{r}
readRDS("StackedBar2.rds")
```

### Those in the West and Midwest are most receptive to the new vaccine, while those in the Northeast and South are more uncertain. 

```{r}
readRDS("RegionVaxMap.rds")
```

### References
